GitHub {{< fa brands github >}}

### 2023-08-11 docs/_repro.qmd
Fix URLs

We recommend two ways of reproducing or inspecting the code of this repository. One option is to clone the [Docker image](https://hub.docker.com/r/gongcastro/cognate-beginnings) we have pused to Dockerhub. A Docker image is just a virtual machine that contains all dependencies, code, and files necessary to run the code. Everything is already installed and setup, you will only have to open [https://localhost:8787](https://localhost:8787) in your browser, and a RStudio session will open for you. This option is more robust (dependencies are difficult to get right when using your own computer), but it also requires Docker to be installed.

>>>>

We recommend two ways of reproducing or inspecting the code of this repository. One option is to clone the [Docker image](https://hub.docker.com/r/gongcastro/cognate-beginnings) we have pused to Dockerhub. A Docker image is just a virtual machine that contains all dependencies, code, and files necessary to run the code. Everything is already installed and setup, you will only have to open [http://localhost:8787](http://localhost:8787) in your browser, and a RStudio session will open for you. This option is more robust (dependencies are difficult to get right when using your own computer), but it also requires Docker to be installed.
